%-------------------------
% Resume in Latex
% Updated for Jason Tello
% Tailored for UI/UX, Product Design, and Apprenticeships
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-3pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jason Tello} \\ \vspace{1pt}
    \small Fairfield / Rio Vista, CA $|$
    \href{mailto:jasontello2003@gmail.com}{\underline{jasontello2003@gmail.com}} $|$
    \href{https://jasontello.com/}{\underline{Portfolio}} $|$
    \href{https://www.linkedin.com/in/jason-tello-123888235/}{\underline{LinkedIn}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Western Governors University}{Jan. 2026}
    {Bachelor of Science in Computer Science}{}

  \resumeSubheading
    {University of California, Merced}{May 2025}
    {Bachelor of Arts in Biology}{GPA: 3.7}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Funfetti Events Website Redesign}{\href{https://jasontello.com/funfetti-events-case-study.html}{\underline{Case Study}}}
{Local Business Website Redesign}{}
\resumeItemListStart
\resumeItem{Redesigned the website for a local event-planning and party-rental business, improving visual direction, service clarity, and the path to request a quote.}
\resumeItem{Audited unclear calls to action, low logo readability, generic imagery, and navigation that did not prioritize booking.}
\resumeItem{Iterated from an early structure prototype into a brighter final direction after stakeholder feedback called for more color and visual energy.}
\resumeItem{Directed an AI-assisted responsive prototype in Codex, reviewing HTML/CSS/JavaScript output for service cards, gallery interactions, and quote-request flows.}
\resumeItemListEnd

\resumeSubheading
{Open Source San Jose Homepage Redesign}{\href{https://jasontello.github.io/BizzNestDesignAssessment/}{\underline{Live Demo}}}
{UI/UX Design Project}{}
\resumeItemListStart
\resumeItem{Redesigned a nonprofit homepage to improve visual hierarchy, content organization, and call-to-action placement.}
\resumeItem{Reorganized key homepage content around mission, community impact, programs, and clearer paths for visitors to get involved.}
\resumeItem{Proposed responsive UI solutions focused on accessibility, information architecture, readability, and volunteer conversion.}
\resumeItemListEnd

\resumeSubheading
{Personal Profile Platform Feature Design}{\href{https://jasontello.github.io/bizznest-linktree-assessment/}{\underline{Live Demo}}}
{Product / UI Design Project}{}
\resumeItemListStart
\resumeItem{Designed a responsive profile-link platform concept and used AI-assisted prototyping to explore layout, content hierarchy, and interaction states.}
\resumeItem{Created editable profile states for colors, links, and layout choices so users could personalize the page without changing code.}
\resumeItem{Reviewed and refined HTML/CSS/JavaScript behavior while focusing on navigation, responsiveness, and information hierarchy.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{IT Asset Management Coordinator}{Mar. 2026 -- Jun. 2026}
{ComputerCare}{Stockton, CA}
\resumeItemListStart
\resumeItem{Use NetSuite, ShipJunction, FedEx Ship Manager, and Jira to process device workflows, verify orders, and maintain records.}
\resumeItem{Troubleshoot work-order discrepancies, check system records, and coordinate exception-based workflows with clear documentation.}
\resumeItemListEnd

\resumeSubheading
{Product Innovation Extern}{Jul. 2026 -- Aug. 2026}
{BeReal Product Innovation Externship}{Remote}
\resumeItemListStart
\resumeItem{Designing and prototyping a new social app feature concept focused on improving user engagement and monthly active users, while mapping user behavior patterns and friction points.}
\resumeItem{Analyzing competitor experiences across TikTok, Instagram, and Snapchat while developing feature ideas through journey mapping, prototype flows, iterative feedback, and a stakeholder-style pitch deck.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Design}{: Figma, visual hierarchy, typography, responsive design, information architecture, accessibility principles, UI design} \\
\textbf{UX Process}{: user flows, wireframing, usability audits, heuristic review, interaction design, portfolio case studies} \\
\textbf{Prototyping}{: Codex, AI-assisted front-end prototyping, HTML/CSS/JavaScript literacy, responsive layout review, browser debugging} \\
\textbf{Tools}{: Figma, GitHub, Jira, Google Workspace, Microsoft Office, NetSuite, ShipJunction, FedEx Ship Manager} \\
}}
\end{itemize}

\end{document}
